
    \documentclass[a4paper,10pt]{article}
    \usepackage[utf8]{inputenc}
    \usepackage{geometry}
    \usepackage{enumitem}
    \usepackage{titlesec}
    \usepackage{hyperref}
    \usepackage{xcolor}
    \usepackage{multicol}
    \usepackage{parskip}
  
    \geometry{a4paper, margin=0.5in}
  
    \titleformat{\section}{\Large\bfseries}{}{0em}{}[\titlerule]
    \titleformat{\subsection}{\large\bfseries}{}{0em}{}
  
    \hypersetup{
        colorlinks=true,
        linkcolor=black,
        filecolor=black,      
        urlcolor=black,
    }
  
    \newcommand{\resumeItem}[2]{
      \item\textbf{#1}{: #2}
    }
    \newcommand{\resumeSubheading}[4]{
      \item
        \textbf{#1} \hfill #2 \\
        \textit{#3} \hfill \textit{#4}
    }
    \newcommand{\resumeSubSubheading}[2]{
        \item
        \textbf{#1} \hfill #2
    }
  
    \begin{document}
  
    \begin{tabbing}
    \hspace{4in} \= \kill
    {\Huge \textbf{Ritesh Girase}} \\
    \href{mailto:riteshgirasecode@gmail.com}{riteshgirasecode@gmail.com} \> 
    \hspace{1.8in}
    \href{https://www.linkedin.com/}{LinkedIn} \\
    Nashik, Maharashtra, India \> \hspace{1.85in}\href{https://github.com}{GitHub} \\ 
    9552566981 \\
    \end{tabbing}
    \vspace{-0.4cm}
  
    \section*{Summary}
    \noindent
    I am a passionate AI and Data Science student with hands-on experience in full-stack development. I thrive in problem-solving, tackling projects like React-based applications, and continuously learning new technologies. I'm dedicated to building impactful solutions and eager to grow in the tech industry.
    \vspace{-0.5em}
  
    \section*{\textbf{Education}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        
        \resumeSubheading
            {State Board}{12th 87.64 \%}
            {Bytco College, Nashik}{2021}
        \vspace{-0.1em}
        \resumeSubheading
            {SPPU}{BE 9.15 spga}
            {MET Bhujbal Knowledge City, Nashik}{2025}
        \vspace{-0.1em}
    \end{itemize}
    \vspace{-0.5em}
  
    \section*{\textbf{Work Experience}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        
        \resumeSubheading
            {Full Stack Web Developer}{12/10/2023 - 20/1/2024}
            {Weoto Technologies Ltd., Nashik}{}\\
            {During my internship at Weoto Technologies Pvt. Ltd., I gained practical experience as a Full-Stack Developer, contributing to the development of web applications. I worked with various technologies, enhancing my skills in frontend development, backend integration, and collaborating in an agile environment. This experience sharpened my problem-solving abilities and strengthened my understanding of building scalable and efficient software solutions.}{}
        \vspace{-0.100em}
    \end{itemize}
    \vspace{-0.5em}
  
    \section*{\textbf{Projects}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        
        \resumeSubheading
            {Pokedex Web Application}{1/2/2023}
            {\href{https://www.linkedin.com/feed/ }{Project Link}}{}\\ \\
            {Developed a dynamic Pokedex web application using React and TypeScript, allowing users to search and view detailed information about various Pokémon. Integrated an external API to fetch Pokémon data and displayed essential details like abilities, moves, and statistics. Focused on implementing responsive UI with Material-UI, ensuring smooth interaction and a user-friendly experience across devices.}{}
        \vspace{0.20em}
        \resumeSubheading
            {Student QR Code System}{}
            {\href{}{}}{}\vspace{0.5em} \\
            {The Student QR Code System is designed to simplify student identification and streamline processes in educational environments. This system generates unique QR codes for each student, allowing them to access various resources, mark attendance, and gain easy access to class materials or assignments. The system is developed to improve efficiency and security, ensuring that all students have quick and reliable access to important school functions.}{}
        \vspace{0.20em}
    \end{itemize}
    \vspace{-0.5em}
  
    \section*{\textbf{Skills}}\noindent
    \textbf{C} \hspace{1em}\textbf{C++} \hspace{1em}\textbf{JAVA} \hspace{1em}\textbf{PYTHON} \hspace{1em}\textbf{JAVASCRIPT} \hspace{1em}\textbf{HTML} \hspace{1em}\textbf{CSS}
    \vspace{0.5em}

  
    \section*{\textbf{Certifications and Awards}}
    \begin{itemize}[leftmargin=0.15in, label={}]
        
        \resumeSubSubheading{DSA using JAVA : NPTEL}{2022}
        
        \vspace{-0.1em}
    \end{itemize}
  
    \end{document}
    